---
title: "Analysis of NEON Woody Plant Vegetation Structure Data"
author: "Sophie Lyth"
date: "2020-05-07"
output: 
  html_document:
    toc: true
    toc_float: true
    theme: spacelab
    highlight: tango
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Background 

This data product contains the quality-controlled, **native sampling resolution data from in-situ measurements of live and standing dead woody individuals and shrub groups, from all terrestrial NEON sites with qualifying woody vegetation**. The exact measurements **collected per individual depend on growth form**, and these measurements are focused on enabling biomass and productivity estimation, estimation of shrub volume and biomass, and calibration / validation of multiple NEON airborne remote-sensing data products.

In general, **comparatively large individuals that are visible to remote-sensing instruments are mapped, tagged and measured, and other smaller individuals are tagged and measured but not mapped**. Smaller individuals may be subsampled according to a nested subplot approach in order to standardize the per plot sampling effort. Structure and mapping data are reported per individual per plot; sampling metadata, such as per growth form sampling area, are reported per plot.

## Data

```{r, echo=FALSE, message=FALSE, warning=FALSE}
knitr::read_chunk(here::here("analysis.R"))
```

```{r analysis-setup}

```

```{r}
summary(individual)
```

```{r}
DT::datatable(individual)
```
```{r analysis-filter-data}

```

```{r analysis-set-factor-levels}

```

```{r analysis-fig1-barplot, fig.cap="Figure 1: Counts of growth forms"}

```

```{r analysis-fig2-violinplots}

```

```{r analysis-lm-overall}

```

```{r analysis-lm-fig3-overall}

```

```{r analysis-lm-growth}

```

```{r analysis-m-fig4-growth}

```
